a and generators

### 2022-08-01 documentos/answer_referees_PRA.txt

*********************************************************************
3, I find this sentence “Let the components of \beta be such that
\beta_l =\beta\delta_lk for a particular particle index k, with \beta
such that a_\alpha_k\beta  = 1” rather confusing.

Answer:
We agree, the statement was confusing. We are now providing a 
new (and hopefully better) explanation.

*********************************************************************
4, Although two mathematical decoherence models are given, the
physical motivation of studying this general many qubit PCE channel is
not quite clear? It also would be better to motivate it in the
beginning.

Answer:
This paper grew from the sheer curiosity of why, for a single qubit, some
projections are allowed and others not. After some time, the beautiful 
mathematical structure presented in this paper appeared. Indeed some 
motivations might be presented, however the main one is simply to gain a 
deeper understanding of quantum channels in a multiparticle setting.
We have put together a modified introduction that reflects that point 
of view, but also addresses the referee's concern, see list of changes.

@@

*********************************************************************
}}}

Answer to of the Second Referee {{{
----------------------------------------------------------------------

*********************************************************************
Could you shed more light on the physical motivation for this study?

Answer:
This paper grew from the sheer curiosity of why, for a single qubit, some
projections are allowed and others not. After some time, the beautiful 
mathematical structure presented in this paper appeared. Indeed some 
motivations might be presented, however the main one is simply to gain a 
deeper understanding of quantum channels in a multiparticle setting.
We have put together a modified introduction that reflects that point 
of view, but also addresses the referee's concern, see list of changes.

*********************************************************************
How do you think the scheme would work for qudits in dimensions of
Hilbert spaces which are not 2^n? Of course, I understand that your
results are pertinent to basis of Pauli tensors, but I am curious to
know your thoughts on the same.

@@

Answer:
This is clearly an interesting question. The generalization is not totally 
direct, and requires some mathematical work.  This is why we did not
present results in this paper, however we will hopefully present a generalization 
for arbitrary dimension. Some care must be taken as some results depend on the
field structure of the set {0,1}, which will not be available for arbitrary 
$d$.

*********************************************************************

}}}

List of changes {{{
* Added to the second paragraph of the intro the following text:
    The main task which we perform in this paper is the identification of the
    conditions which an arbitrary PCE map must satisfy in order to be completely
    positive. The answer turns out to involve a strikingly simple and unexpected
    mathematical structure that is exploited to gain deeper understanding
    on aforementioned channels, as we show in section \ref{sec:vector_spaces}. This
    structure allows for example to describe such channels with a much reduced
    set of parameters (as compared to specifying a list of all erased Pauli
    components) or to define an
    interesting semigroup structure on the set of all PCE channels. 
    Additionally, these channels, are in a sense the simplest possible channels,
    and as such can be used as building bocks of more general channels, for
    instance through convex combination or composition.
    To summarize succinctly the final result, we show that it is possible
    to assign to every Pauli string a simple PCE channel, obtained by extending
    the system with an ancilla of a single qubit, acting on the combined system by
    a unitary involving the Pauli string and tracing over the ancilla. It then
    follows from our results that all PCE channels arise from such
    channels by composition.
* Between eq. (2) and eq. (3) we replaced 
    Not every such operation  is a quantum channel;
with 
    Not every such map  is a quantum channel;

### 2022-08-01 documentos/intro.tex
I was wrong...

\par
In this work we present a generalization of idempotent Pauli channels, \ie{}
the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
channel and the identity channel, to the case of $N$ qubits. 
% \cpnote{Mencionar decoherencia} 
The generalization is done by extending
Pauli observables to \textit{Pauli strings} (tensor products of Pauli
matrices)~\cite{KIMURA2003339,Lawrence2002}. The resulting maps are unital and
diagonal in the Pauli strings' basis.
In addition, these channels describe the decoherence process in a similar way
as the aforementioned
ones for the single-qubit case.
From now on we refer to these maps as \textit{Pauli component erasing} (\pce{})
maps. We
derive necessary and sufficient conditions for such mappings to be completely
positive and trace-preserving, thus, showing which idempotent operations are valid
quantum channels (\pce{} channels). Additionally, we characterize the algebraic
properties of the set of \pce{} channels, showing that it is equipped
with a semigroup structure, which is later used to derive physical
implementations.
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
the properties of quantum channels needed to proceed with the definition 
of 
% the tools to unders
% refreshing of quantum channels theory and the definition of 
\pce{} maps. 
In section~\ref{sec:math} we diagonalize analytically the Choi matrix for
arbitrary \pce{} maps and characterize their complete positivity by
interpreting \pce{} quantum channels as finite vector subspaces.
% In
% section~\ref{sec:math} we diagonalize analytically the Choi matrix for
% arbitrary \pce{} maps and characterize \janote{the} completely positive maps by interpreting
% \pce{} maps \janote{quantum channels?} as finite vector spaces. 
We study the
generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well as Kraus operators of the generators.
% 
To finish, we conclude and discuss future perspectives in
section~\ref{sec:conclusions}.
% }}}

>>>>

In this work we present a generalization of idempotent Pauli channels, \ie{}
the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
channel and the identity channel, to the case of $N$ qubits. 
% \cpnote{Mencionar decoherencia} 
The generalization is done by extending
Pauli observables to \textit{Pauli strings} (tensor products of Pauli
matrices)~\cite{KIMURA2003339,Lawrence2002}. The resulting maps are unital and
diagonal in the Pauli strings' basis. 
We shall in the following refer to 
such maps as {\em Pauli component erasing maps} (\pce{} maps)
The main task which we perform in this paper is the identification of the
conditions which an arbitrary \pce{} map must satisfy in order to be completely
positive. The answer turns out to involve a strikingly simple and unexpected
mathematical structure that is exploited to gain deeper understanding
on aforementioned channels, as we show in section \ref{sec:vector_spaces}. This
structure allows for example to describe such channels with a much reduced
set of parameters (as compared to specifying a list of all erased Pauli
components) or to define an
interesting semigroup structure on the set of all \pce{} channels. 
Additionally, these channels, are in a sense the simplest possible channels,
and as such can be used as building bocks of more general channels, for
instance through convex combination or composition.
To summarize succinctly the final result, we show that it is possible
to assign to every Pauli string a simple \pce{} channel, obtained by extending
the system with an ancilla of a single qubit, acting on the combined system by
a unitary involving the Pauli string and tracing over the ancilla. It then
follows from our results that {\em all\/} \pce{} channels arise from such
channels by composition.

%In addition, these channels describe the decoherence process in a similar way
%as the aforementioned
%ones for the single-qubit case.
%Additionally, we characterize the algebraic
%properties of the set of \pce{} channels, showing that it is equipped
%with a semigroup structure, which is later used to derive physical
%implementations.

%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
the properties of quantum channels needed to proceed with the definition 
of 
% the tools to unders
% refreshing of quantum channels theory and the definition of 
\pce{} maps. 
In section~\ref{sec:math} we diagonalize analytically the Choi matrix for
arbitrary \pce{} maps and characterize their complete positivity by
interpreting \pce{} quantum channels as finite vector subspaces.
% In
% section~\ref{sec:math} we diagonalize analytically the Choi matrix for
% arbitrary \pce{} maps and characterize \janote{the} completely positive maps by interpreting
% \pce{} maps \janote{quantum channels?} as finite vector spaces. 
We study the
generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well as Kraus operators of the generators.
% 
To finish, we conclude and discuss future perspectives \flnote{and possible generalizations} in
section~\ref{sec:conclusions}.
% }}}
